Astr 513: Final Project

### 2016-05-02 Final_Project/ms.tex
Added linebreaks and removed some of my comments. Added a new comment in section 4.0.

\subsection{Covariances}
\label{sec:covariances}
\TM{A subsection that explains how the covariance matrix looks. Basically
  a brief discussion about how it was made.}
\LC{Wrote about Rest's cov matrix. Still need description of Betoule's.}

@@

\section{Distance Modulus Model}
\label{sec:model}
\TM{This explains how to go from a cosmology to $\mu(z)$.}
\LC{Need more here but I wrote most of the relevant eqns}
The main objective of \citet{betoule2014} and \citet{rest2014} is to place constraints on cosmological parameters $\Omega_M$, $\Omega_\Lambda$, and $w$. In order to so, we must examine the relationship between distance modulus and cosmology. The distance modulus $\mu$ is determined from the luminosity distance $d_L$ by 
\begin{equation}
\label{eq:mu_dL}
\mu=5 \text{log}(d_L)+25. 
\end{equation}
The luminosity distance depends on the cosmology by 
\begin{equation}
\label{eq:luminosityDistance}
d_L(z; w, \Omega_M, \Omega_\Lambda, H_0)= (1+z)|\Omega_k|^{-1/2}\mathcal{S}_{k}\displaystyle\left[c|\Omega_k|^{1/2}\int_{0}^{z}\frac{dz'}{H(z')}\right],
\end{equation}
where $\Omega_k \equiv 1-\Omega_M-\Omega_{\Lambda}$. The function $\mathcal{S}_{k}$ depends on the curvature density $\Omega_k$ in that 
\[
    \mathcal{S}_{k}= 
\begin{cases}
    \text{sin}(x),&  \Omega_k < 0\\
    x,& \Omega_k = 0\\
    \text{sinh}(x),& \Omega_k > 0
\end{cases}
\]
and the function $H(z)$ is 
\begin{equation}
\label{eq:hubbleFunction}
H(z)= H_0\displaystyle\left[\Omega_M(1+z)^3+\Omega_{\Lambda}(1+z)^{3(1+w)}+\Omega_k(1+z)^2\right]^{1/2}.
\end{equation}
Three (?) cosmologies are of interest to us: \LC{Not sure which ones we're interested in. $\Lambda CDM$, $\Omega_M=1$, ?}

>>>>

\subsection{Covariances}
\label{sec:covariances}
\LC{Wrote about Rest's cov matrix. Still need description of Betoule's.}

@@

\section{Distance Modulus Model}
\label{sec:model}
\LC{Need more here but I wrote most of the relevant eqns}
The main objective of \citet{betoule2014} and \citet{rest2014} is 
to place constraints on cosmological parameters $\Omega_M$, $\Omega_\Lambda$, 
and $w$. In order to so, we must examine the relationship between distance 
modulus and cosmology. The distance modulus $\mu$ is determined from 
the luminosity distance $d_L$ by 
\begin{equation}
\label{eq:mu_dL}
\mu=5 \text{log}(d_L)+25. 
\end{equation}
The luminosity distance depends on the cosmology by 
\begin{equation}
\label{eq:luminosityDistance}
d_L(z; w, \Omega_M, \Omega_\Lambda, H_0)= (1+z)|\Omega_k|^{-1/2}\mathcal{S}_{k}\displaystyle\left[c|\Omega_k|^{1/2}\int_{0}^{z}\frac{dz'}{H(z')}\right],
\end{equation}
where $\Omega_k \equiv 1-\Omega_M-\Omega_{\Lambda}$. The function 
$\mathcal{S}_{k}$ depends on the curvature density $\Omega_k$ in that 
\[
    \mathcal{S}_{k}= 
\begin{cases}
    \text{sin}(x),&  \Omega_k < 0\\
    x,& \Omega_k = 0\\
    \text{sinh}(x),& \Omega_k > 0
\end{cases}
\]
and the function $H(z)$ is 
\begin{equation}
\label{eq:hubbleFunction}
H(z)= H_0\displaystyle\left[\Omega_M(1+z)^3+\Omega_{\Lambda}(1+z)^{3(1+w)}+\Omega_k(1+z)^2\right]^{1/2}.
\end{equation}
Three (?) cosmologies are of interest to us: 
\LC{Not sure which ones we're interested in. $\Lambda CDM$, $\Omega_M=1$, ?}
\TM{I think there are only two, one with $\Omega_k=0$ and one with it
  being unconstrained.}
